% \pagestyle{empty}
% \begin{center}
% \vspace*{4em}
% \zihao{3} \heiti 微生物土壤运移模型的求解及仿真软件编制
% \vspace*{3em}
% \end{center}
% \zihao{-4}
% \noindent 摘\quad要: 本研究对微生物在土壤中运移过程进行建模,具体采用对流扩散反应模型来描述微生物的运动.
% 		     并对它的定解条件进行了讨论和分析.考虑到重力对水流扩散的影响,将一维上的对流扩散反应
% 		     方程拓展到三维空间上,建立了三维空间的立体模型.
% \noindent {\heiti 关键字: 计算 有限差分法 仿真}

\chapter*{\heiti 微生物土壤运移模型的求解及仿真软件编制\\[1.5em]
摘\qquad 要}
本研究对微生物在土壤中运移过程进行建模,具体采用对流扩散反应模型来描述微生物的运动.
并对它的定解条件进行了讨论和分析.考虑到重力对水流扩散的影响,将一维上的对流扩散反应
方程拓展到三维空间上,建立了三维空间的立体模型.得到模型后,本文分别对有限差分法中的
各类差分格式进行了研究并在模型上进行了应用,得到了最优的求解方法.最后,尝试编制仿真程序,
对微生物的运移过程进行模拟与仿真.\par
本文重点对偏微分方程,尤其是对流扩散反应方程的数值差分格式进行了研究.讨论了抛物线型
和双曲型方程的差分方法,也讨论了具有双曲特性的抛物线型偏微分方程的差分格式,证明了它们
的稳定性和精确度.最后,讨论了算子分裂法,建立了三维对流扩散反应方程的差分格式并对稳定性
和精确度进行了讨论.\par
\vspace*{\baselineskip}
{\heiti 关键字: 计算\quad 有限差分法\quad 对流扩散反应方程}
\clearpage{\pagestyle{empty}\cleardoublepage}
\chapter*{\bfseries THE SOLUTIONS OF MODEL FOR MOVEMENT OF MICROORGINISMS AND DEVELOPMENT OF SIMULATION PROGRAM\\[2em]
ABSTRACT}

% The research aim to build the mathematic model for the moving process of
% some microorganism in the soil,which can be described by the 
% reaction--diffusion--convection systems,and we discuss the definite condition of 
% the partial differential equation.\par Considering the effect of gravity for the  proliferation of water
% in soil,we build the three dimensional model based on one dimensional model.After that,we attempt to
% make the solutions with finite difference method,and have the best method for solving the models.
% Finally, we attempt to build the program to simulate the process,and show the dynamic process on
% the screen.\par
% We discuss the numberial solutions of partial differential equations,including parabolic curve and
% hyperbolic curve equations.and we prove the steady and accuercy for the scheme.and then we discuss
% The operator splitting method,build the 3d module for RDC Systems,and prove the steady and accuercy 
% for the diffusion scheme.\par
The research of microorganisms in soil modeling process aimed to build the convection-diffusion-reaction model to describe the movement of microorganisms.
And the boundary conditions are discussed and analyzed. Taking into account the influence of gravity
on the water diffusion, on the one-dimensional convection-diffusion reaction equation extended to 
three-dimensional space, create a three-dimensional three-dimensional model paper finite difference 
respectively law of the various types were studied and the difference scheme on the model has been 
applied to obtain the optimal solution method. Finally,try preparing emulation program on microbial
migration process modeling and simulation.\par
% This paper focuses on the study of numerical difference schemes for numberpartial differential equations,in particular convection-diffusion reaction
% equation.Discusses parabolic and hyperbolic differential equations method,also discussed with hyperbolic characteristic parabolic partial differential 
% equations difference scheme proved their stability and accuracy. 
Finally, we discuss the operator splitting method, a three-dimensional convection-diffusion
reaction equation of the differential form and stability and accuracy are discussed.
\vspace*{1.5em}\par
\noindent\textbf{Key Words:Computing;finite difference method;reaction-diffusion-convection systems}